Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Polish implementation of Doctest

To extract evidence from Haddock comments,
Doctest initially used the Haddock API.
Since each release of Haddock only supports the latest version of GHC,
it was difficult to support old versions of GHC with Doctest.
Doctest now uses the GHC API directly for portability.

@@

\begin{quote}
    TBD: We read both, stdout + stderr from GHCi and compare that with the
    expected result.  On Windows, only stdout works (IIRC, when an
    example causes output to stderr on windows, doctest exits with an
    error, see http://hackage.haskell.org/trac/ghc/ticket/5761).

    sol: relevant?
\end{quote}

Doctest uses GHCi to verify examples.  Verification is done by
comparing the expected output given in the Haddock comment with the
actual output of GHCi.  Since verification is based on string
comparison, exceptions can be handled.

@@

\noindent QuickCheck and GHCi are used to test properties.  Before we
test a property, we bring the module that contains the Haddock comment
from which we extracted the property into scope.

Implicitly quantified properties need to be closed before they can be
tested.  This requires the following steps.
\begin{enumerate}
    \item
        Find all free variables of the property
    \item
        Try to lookup each free variable in the module context
    \item
        Close the property over all free variables, for which lookup
        failed
\end{enumerate}

@@

The implementation is fully functional, and it will be included in the
next release of Doctest.

>>>>

Doctest uses the GHC API to extract properties and examples from
Haddock comments, and uses GHCi to test them.
Before testing, Doctest brings the module that contains the Haddock
comment from which the evidence was extracted into scope.

@@

Verification of examples is done by
comparing the expected output given in the Haddock comment with the
actual output of GHCi.

@@

QuickCheck is used to test properties.
Implicitly quantified properties need to be closed before they can be
tested.  This requires the following steps.
\begin{enumerate}
    \item
        Find all free variables of the property.
    \item
        Try to lookup each free variable in the module context.
    \item
        Close the property over all free variables, for which lookup
        failed.
\end{enumerate}

@@

\noindent The implementation is fully functional, and it will be included in the
next release of Doctest.
